Assessing primitives performance\\ on multi-stage execution

### 2018-05-10 paper.tex
more on bench details

\paragraph{Optimization potential on large strings comparison}
The plugins come with an overhead due to the cross-file inlining and the passage through an InterpreterProxy, like said in Section \ref{sec:implem_cmp}. This is one of the factor explaining the performance gap between these versions and the Slang and Slang+JIT ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure \ref{fig:Asm}). However, the switch overhead is still noticeable in the PureSlang implementation when strings of 100 characters are compared: PureSlang is 15.8 times faster while Slang+JIT is 16.8 times faster. This is not the case anymore on 1000-characters strings.
This last observation only applies to the GCC results. The LLVM version

\paragraph{Control over generated code}
One could notice a rather striking performance difference between the 2 compilers: when compiling with GCC, the performances between the PureSlang and Slang+JIT implementations are really close for long strings (100 characters and longer), with respectively 24,42 and 24,48 relative speed-up factors for a 1000-characters string. Yet they greatly differ when LLVM is used, with respectively 13,44 and 26,40 relative speed-up factors.

@@

>>>>

\paragraph{Optimization potential on large strings comparison}
The plugins come with an overhead \sk{not an overhead when it comes to inlining. Just not optimized. need rephrasing} due to the cross-file inlining and the passage through an InterpreterProxy, like said in Section \ref{sec:implem_cmp}. This is one of the factor explaining the performance gap between these versions and the Slang and Slang+JIT ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure \ref{fig:Asm}). However, the switch overhead is still noticeable in the PureSlang implementation when strings of 100 characters are compared: PureSlang is 15.8 times faster while Slang+JIT is 16.8 times faster. This is not the case anymore on 1000-characters strings.
This last observation only applies to the GCC results: the code generated by the LLVM compiler induces a longer execution time, as explained in the next paragraph. \sk{is it legal to ref that way?}
\paragraph{Control over generated code}
One could notice a rather striking performance difference between the 2 compilers: when compiling with GCC, the performances between the PureSlang and Slang+JIT implementations are really close for long strings (100 characters and longer), with respectively 24,42 and 24,48 relative speed-up factors for a 1000-characters string. Yet they greatly differ when LLVM is used, with respectively 13,44 and 26,40 relative speed-up factors.

@@

\todo{add conclusion}
